Parallel Computing for Constrained Global Optimization Problems

### 2018-12-11 2019/ICCS_Barkalov/ICCS_Paper.tex

%%%%%%%%%%%%%%%%%%%%%%% file template.tex 
%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn

@@

\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{multirow}
%
%\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
 \journalname{The Journal of Supercomputing}
%
\begin{document}

\title{Parallel Computing for Constrained Global Optimization Problems
\thanks{The study was supported by the Russian Science Foundation, project No 16-11-
10150.}
}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\author{Konstantin Barkalov          \and
        Ilya Lebedev %etc.
}

@@

\institute{K. Barkalov  \at
               Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia \\
              \email{konstantin.barkalov@itmm.unn.ru} 
           \and
           I. Lebedev \at
					Lobachevsky State University of Nizhni Novgorod, Nizhni 
Novgorod, Russia \\
							\email{ilya.lebedev@itmm.unn.ru} 
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{abstract}
This paper considers a parallel algorithm for solving multiextremal problems with non-convex 
constrains. Within the framework of the approach proposed here, the solution of the initial 
multidimensional problem is reduced to solving a set of linked one-dimensional problems in 
parallel. The parallelization scheme does not require a single control process since the solution of 
any one-dimensional problem is a solution of the initial multidimensional one. The non-convex 
constraints are accounted for by a novel index scheme without utilizing the ideas of penalty 
functions. The efficiency of the parallel algorithm was confirmed experimentally by solving 
numerically several hundred multidimensional multiextremal problems with non-convex 
constrains generated randomly.
\keywords{Global optimization \and Constrained problems \and Non-convex constraints \and 
Dimensionality reduction \and Parallel algorithms}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}

@@

%Another example is the optimal control problem described through system of ordinary 
%differential equations with a certain matrix $A$ on the right side \cite{Balandin2017}. It is only 
%possible to calculate the optimality criteria for these problems if the matrix $A$ is a Hurwitz 
%matrix, i.e. every eigenvalue of $A$ has a strictly negative real part. Otherwise, the value of the 
%criteria is indeterminate.

@@

% Non-BibTeX users please use
\begin{thebibliography}{}

\bibitem{RefFerreiro}
Ferreiro, A.M., Garcia, J.A., Lopez-Salas, J.G., Vazquez, C.: An efficient implementation of 
parallel simulated annealing algorithm in GPUs. J. Glob. Optim. 57(3), 863--890 (2013)

\bibitem{RefZhu}
Zhu, W.: Massively parallel differential evolution--pattern search optimization with graphics 
hardware acceleration: an investigation on bound constrained optimization problems. J. Glob. 
Optim. 50(3), 417--437 (2011).

\bibitem{Korosec}
Koro\v sec, P., Vajter\v sic, M.,  \v Silc, J., Kutil, R.: Multi-core implementation of the 
differential ant-stigmergy algorithm for numerical optimization. J. Supercomput. 63(3), 757--
772 (2013)

\bibitem{Guerrero}
Guerrero, G.D., Cecilia, J.M., Llanes, A. et al.: Comparative evaluation of platforms for parallel 
Ant Colony Optimization. J. Supercomput. 69(1) 318--329 (2014)

@@

\bibitem{Paulavicius2011}
Paulavi\v cius, R., \v Zilinskas, J., Grothey, A.: Parallel branch and bound for global 
optimization with combination of Lipschitz bounds. Optim. Methods Softw. 26(3), 487--498 
(2011)

\bibitem{Evtushenko2013}
Evtushenko, Y.G., Posypkin, M.A.: A deterministic approach to global box-constrained 
optimization. Optim. Lett. 7(4), 819--829 (2013)

@@

%\bibitem{Balandin2017}Balandin, D.V., Kogan, M.M.: Pareto-optimal generalized $H_2$-control and vibroprotection problems. Automation and Remote Control. 78(8), 1417--1429 (2017)

\bibitem{Sergeyev2001}
Sergeyev, Y.D., Famularo D., Pugliese P. Index Branch-and-Bound Algorithm for Lipschitz 
univariate global optimization with multiextremal constraints. J. Glob. Optim. 21(3), 317--341 
(2001)

\bibitem{Barkalov2002}
Barkalov, K.A., Strongin, R.G.: A global optimization technique with an adaptive order of 
checking for constraints. Comput. Math. Math. Phys. 42(9), 1289--1300 (2002)

@@

\bibitem{Gaviano2003}
Gaviano, M., Lera, D., Kvasov, D.E., Sergeyev, Ya.D.: Software for generation of classes of 
test functions with known local and global minima for global optimization. ACM Trans. Math. 
Software 29, 469--480 (2003)

\bibitem{Gergel2017}
Gergel, V.: An approach for generating test problems of constrained global optimization. 
LNCS. 10556, 314--319 (2017)

@@

\bibitem{Sidorov2015}
Gergel, V., Sidorov, S.: A two-level parallel global search algorithm for solution of 
computationally intensive multiextremal optimization problems. LNCS. 9251, 505--515 (2015)

\bibitem{Barkalov2017}
Barkalov, K., Lebelev, I.: Comparing Two Approaches for Solving Constrained Global 
Optimization Problems. LNCS. 10556, 301--306 (2017)

\bibitem{6_Gergel2009}
Strongin, R.G., Gergel, V.P., Barkalov, K.A.: Parallel methods for global optimization problem 
solving. Journal of instrument engineering. 52, 25--33 (2009) (In Russian)

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex 
%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%
%

%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
\documentclass{llncs}

@@

% flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage[misc,geometry]{ifsym}

\usepackage{amsmath}

%
%\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with

%
\begin{document}

\mainmatter

\title{Parallel Computing for Constrained Global Optimization Problems}

%\subtitle{Do you have a subtitle?\\ If so, write it here}

@@

\author{Konstantin Barkalov \Letter \and
        Ilya Lebedev %\Letter
\\
\email{konstantin.barkalov@itmm.unn.ru}
%\\
%\email{ilya.lebedev@itmm.unn.ru}
}

@@

\institute{
Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia
}

@@

\begin{abstract}
This paper considers a parallel algorithm for solving multiextremal problems with non-convex 
constrains. Within the framework of the approach proposed here, the solution of the initial 
multidimensional problem is reduced to solving a set of linked one-dimensional problems in 
parallel. The parallelization scheme does not require a single control process since the solution of 
any one-dimensional problem is a solution of the initial multidimensional one. The non-convex 
constraints are accounted for by a novel index scheme without utilizing the ideas of penalty 
functions. The efficiency of the parallel algorithm was confirmed experimentally by solving 
numerically several hundred multidimensional multiextremal problems with non-convex 
constrains generated randomly.

\keywords global optimization, constrained problems, non-convex constraints, 
dimensionality reduction, parallel algorithms.
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}

\end{abstract}

\section{Introduction}\label{intro}

@@

Another example is the optimal control problem described through system of ordinary 
differential equations with a certain matrix $A$ on the right side \cite{Balandin2017}. It is only 
possible to calculate the optimality criteria for these problems if the matrix $A$ is a Hurwitz 
matrix, i.e. every eigenvalue of $A$ has a strictly negative real part. Otherwise, the value of the 
criteria is indeterminate.

@@

\section*{Acknowledgments}
The study was supported by the Russian Science Foundation, project No 16-11-10150.

% Non-BibTeX users please use
\begin{thebibliography}{99}

\bibitem{RefFerreiro}
Ferreiro, A.M., Garcia, J.A., Lopez-Salas, J.G., Vazquez, C.: An efficient implementation of 
parallel simulated annealing algorithm in GPUs. J. Glob. Optim. \textbf{57}(3), 863--890 (2013)

\bibitem{RefZhu}
Zhu, W.: Massively parallel differential evolution--pattern search optimization with graphics 
hardware acceleration: an investigation on bound constrained optimization problems. J. Glob. 
Optim. \textbf{50}(3), 417--437 (2011).

\bibitem{Korosec}
Koro\v sec, P., Vajter\v sic, M.,  \v Silc, J., Kutil, R.: Multi-core implementation of the 
differential ant-stigmergy algorithm for numerical optimization. J. Supercomput. \textbf{63}(3), 757--
772 (2013)

\bibitem{Guerrero}
Guerrero, G.D., Cecilia, J.M., Llanes, A. et al.: Comparative evaluation of platforms for parallel 
Ant Colony Optimization. J. Supercomput. \textbf{69}(1) 318--329 (2014)

@@

\bibitem{Paulavicius2011}
Paulavi\v cius, R., \v Zilinskas, J., Grothey, A.: Parallel branch and bound for global 
optimization with combination of Lipschitz bounds. Optim. Methods Softw. \textbf{26}(3), 487--498 
(2011)

\bibitem{Evtushenko2013}
Evtushenko, Y.G., Posypkin, M.A.: A deterministic approach to global box-constrained 
optimization. Optim. Lett. \textbf{7}(4), 819--829 (2013)

@@

\bibitem{Balandin2017}Balandin, D.V., Kogan, M.M.: Pareto-optimal generalized $H_2$-control and vibroprotection problems. Automation and Remote Control. \textbf{78}(8), 1417--1429 (2017)

\bibitem{Sergeyev2001}
Sergeyev, Y.D., Famularo D., Pugliese P. Index Branch-and-Bound Algorithm for Lipschitz 
univariate global optimization with multiextremal constraints. J. Glob. Optim. \textbf{21}(3), 317--341 
(2001)

\bibitem{Barkalov2002}
Barkalov, K.A., Strongin, R.G.: A global optimization technique with an adaptive order of 
checking for constraints. Comput. Math. Math. Phys. \textbf{42}(9), 1289--1300 (2002)

@@

\bibitem{Gaviano2003}
Gaviano, M., Lera, D., Kvasov, D.E., Sergeyev, Ya.D.: Software for generation of classes of 
test functions with known local and global minima for global optimization. ACM Trans. Math. 
Software \textbf{29}, 469--480 (2003)

\bibitem{Gergel2017}
Gergel, V.: An approach for generating test problems of constrained global optimization. 
Lecture Notes in Computer Science. \textbf{10556}, 314--319 (2017)

@@

\bibitem{Sidorov2015}
Gergel, V., Sidorov, S.: A two-level parallel global search algorithm for solution of 
computationally intensive multiextremal optimization problems. Lecture Notes in Computer Science. \textbf{9251}, 505--515 (2015)

\bibitem{Barkalov2017}
Barkalov, K., Lebelev, I.: Comparing Two Approaches for Solving Constrained Global 
Optimization Problems. Lecture Notes in Computer Science. \textbf{10556}, 301--306 (2017)

\bibitem{6_Gergel2009}
Strongin, R.G., Gergel, V.P., Barkalov, K.A.: Parallel methods for global optimization problem 
solving. Journal of instrument engineering. \textbf{52}, 25--33 (2009) (In Russian)
